---
title: "Madison Bee Communities"
author: "Vera Pfeiffer"
date: "January 9, 2019"
output: 
  html_document:
    theme: spacelab
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Desktop/MadBees')
```

## Bee Community Data

This report includes the statistical analyses used to understand the influence of landscape composition and land use history on bee community diversity across a rapidly-growing midwestern american city.  Bees sampled in passive traps known as bee bowls six times across the City of Madison in 2013.

```{r}
getwd()
MadBees<-read.csv("MadBeesBeeBowlsFinal.csv")
xy<-read.csv("xy.csv")
names(MadBees)
```

## Bee species summary

The unique bee species identified in the samples include:

```{r echo=FALSE}
sort(unique(MadBees$Morphospecies))
```

## Bee species subsets by habitat type

```{r}
Soilbees<-subset(MadBees, Habitat=="Soil")
Cavitybees<-subset(MadBees, Habitat=="Cavity")
Woodbees<-subset(MadBees, Habitat=="Wood")
```

#################  Species matrices ####################

```{r}
library(vegan)
MadbeesMAT<-xtabs( ~ MadBees$SiteID + MadBees$Morphospecies, data=MadBees)
SoilbeesMAT<-xtabs( ~ Soilbees$SiteID + Soilbees$Morphospecies, data=Soilbees)
CavitybeesMAT<-xtabs( ~ Cavitybees$SiteID + Cavitybees$Morphospecies, data=Cavitybees)
WoodbeesMAT<-xtabs( ~ Woodbees$SiteID + Woodbees$Morphospecies, data=Woodbees)
```

```{r}
write.csv(MadbeesMAT, "allbees.csv")
write.csv(SoilbeesMAT, "soilbees.csv")
write.csv(CavitybeesMAT, "cavitybees.csv")
write.csv(WoodbeesMAT, "woodbees.csv")
```








