---
title: "Madison Bee Communities"
author: "Vera Pfeiffer"
date: "January 9, 2019"
output: 
  html_document:
    theme: spacelab
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Desktop/MadBees')
```

## Bee Community Data

This report includes the statistical analyses used to understand the influence of landscape composition and land use history on bee community diversity across a rapidly-growing midwestern american city.  Bees sampled in passive traps known as bee bowls six times across the City of Madison in 2013.

```{r}
getwd()
MadBees<-read.csv("MadBeesBeeBowlsFinal.csv")
xy<-read.csv("xy.csv")
names(MadBees)
```

## Bee species summary

The unique bee species identified in the samples include:

```{r echo=FALSE}
sort(unique(MadBees$Morphospecies))
```

## Bee species subsets by habitat type

```{r}
Soilbees<-subset(MadBees, Habitat=="Soil")
Cavitybees<-subset(MadBees, Habitat=="Cavity")
Woodbees<-subset(MadBees, Habitat=="Wood")
```

#################  Species matrices ####################

```{r}
library(vegan)
MadbeesMAT<-xtabs( ~ MadBees$SiteID + MadBees$Morphospecies, data=MadBees)
SoilbeesMAT<-xtabs( ~ Soilbees$SiteID + Soilbees$Morphospecies, data=Soilbees)
CavitybeesMAT<-xtabs( ~ Cavitybees$SiteID + Cavitybees$Morphospecies, data=Cavitybees)
WoodbeesMAT<-xtabs( ~ Woodbees$SiteID + Woodbees$Morphospecies, data=Woodbees)
```

```{r}
write.csv(MadbeesMAT, "allbees.csv")
write.csv(SoilbeesMAT, "soilbees.csv")
write.csv(CavitybeesMAT, "cavitybees.csv")
write.csv(WoodbeesMAT, "woodbees.csv")
```



###################### Abundance ######################


library(vegan)
library(ggplot2)

Aabd<-rowSums(allB[,2:ncol(allB)])
Asp <- specnumber(allB)


ASmod<-plot(log(Asp)~yrA$YrMed)
Devel<-rep("Old",length(Asp))
Devel[which(yrA$YrMed>1960)]<-"New"


BeeData<-data.frame(Aabd,Asp,Devel)


ASmod<-plot(log(Asp)~Devel)
ASmod<-lm(S~PercFor1000+PercImp1000+PercNVeg1000+PercFor200+PercImp200+PercNVeg200+YrMean)

f <- ggplot(BeeData, aes(Devel, Aabd))
f + geom_violin(scale = "area")

f <- ggplot(BeeData, aes(Devel, Asp))
f + geom_violin(scale = "area")


Sabd<-rowSums(soilB[,2:99])
SSp<-rowSums(soilB[,2:99]!=0)


Cabd<-rowSums(cavityB[,2:99])
CSp<-rowSums(cavityB[,2:99]!=0)


Wabd<-rowSums(woodB[,2:99])
WSp<-rowSums(woodB[,2:99]!=0)


DevelC<-rep("Old",length(CSp))
DevelC[which(yrC$YrMed>1961)]<-"New"

DevelW<-rep("Old",length(WSp))
DevelW[which(yrW$YrMed>1961)]<-"New"


Devel01<-rep(0,length(Asp))
Devel01[which(yrA$YrMed>1961)]<-1
DevelC01<-rep(0,length(CSp))
DevelC01[which(yrC$YrMed>1961)]<-1
DevelW01<-rep(0,length(WSp))
DevelW01[which(yrW$YrMed>1961)]<-1

SBeeData<-data.frame(Sabd,SSp,Devel)
WBeeData<-data.frame(Wabd,WSp,DevelW)
CBeeData<-data.frame(Cabd,CSp,DevelC)

AVabdA$Devel01ST<-scale(Devel01,0,1)

f <- ggplot(SBeeData, aes(Devel, Sabd))
f + geom_violin(scale = "area")

f <- ggplot(SBeeData, aes(Devel, SSp))
f + geom_violin(scale = "area")

f <- ggplot(WBeeData, aes(DevelW, Wabd))
f + geom_violin(scale = "area")

f <- ggplot(WBeeData, aes(DevelW, WSp))
f + geom_violin(scale = "area")

f <- ggplot(CBeeData, aes(DevelC, Cabd))
f + geom_violin(scale = "area")

f <- ggplot(CBeeData, aes(DevelC, CSp))
f + geom_violin(scale = "area")



AabdMod<-lm(ASpST~PercFor1000+PercNVeg1000+PercImp1000+PercFor200+PercImp200+PercNVeg200+Devel01ST, data=AVabdA,  na.action = "na.fail")
summary(AabdMod)
vif(AabdMod)
dredge(AabdMod)
ABeeSpmodsel<-dredge(AabdMod,beta = c("none"), rank = "AICc")
avgcoef<-model.avg(ABeeSpmodsel, cumsum(weight) <= .95)
avgcoef
importance(avgcoef)


SabdMod<-lm(SSp~PercFor1000+PercNVeg1000+PercImp1000+PercFor200+PercImp200+PercNVeg200+Devel01, data=AVabdS,  na.action = "na.fail")
summary(SabdMod)
vif(SabdMod)
SabdModmodsel<-dredge(SabdMod,beta = c("none"), rank = "AICc")
avgcoef<-model.avg(SabdModmodsel, cumsum(weight) <= .95)
avgcoef
importance(avgcoef)

WabdMod<-lm(WSp~PercFor1000+PercNVeg1000+PercImp1000+PercFor200+PercImp200+PercNVeg200+Devel01, data=AVabdW,  na.action = "na.fail")
summary(WabdMod)
vif(WabdMod)
WabdModmodsel<-dredge(WabdMod,beta = c("none"), rank = "AICc")
WabdModmodsel
avgcoef<-model.avg(WabdModmodsel, cumsum(weight) <= .95)
avgcoef
importance(avgcoef)


CabdMod<-lm(CSp~PercFor1000+PercNVeg1000+PercImp1000+PercFor200+PercImp200+PercNVeg200+Devel01, data=AVabdC,  na.action = "na.fail")
summary(CabdMod)
vif(CabdMod)
CabdModmodsel<-dredge(CabdMod,beta = c("none"), rank = "AICc")
CabdModmodsel
avgcoef<-model.avg(CabdModmodsel, cumsum(weight) <= .95)
avgcoef
importance(avgcoef)







